---
title: "What's my Game?"
author: "Yuqing Xue  <https://github.com/Testimate/Poker>"
date: "November 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)

# https://blogs.reed.edu/ed-tech/2015/10/creating-nice-tables-using-r-markdown/
library(knitr) #kable
#library(xtable) # xtable: generate LaTeX code to output table into PDF  

library(highcharter)
```

_Dec 5th: Idea: add vertical dash line between the 14th session (Sat) with the 15th session (Thu) to separate my playing mindset as pre-"The Course" era and post-"The Course" era: The Book by Ed Miller_

_Dec 5th: Implementation: create a separate dataset 'Enlightened' instead_

<br>


## My Statistical Analysis for My Poker Statistics

<br>

### 1. Data Preparation

```{r First City Settled!}
#filePath <- file.choose()
filePath <- "/Users/apple/Desktop/YuqingRWork/Poker/DesciplinePokerAtheletes.xlsx"
GoogleSheet <- read_excel(filePath)

Testimate <- GoogleSheet %>% mutate(Date = ymd(Date), #sesStart = ymd_hms(sesStart), sesEnd = ymd_hms(sesEnd),
                             sesLength = round( as.numeric(sesEnd - sesStart), 2), #directly make substraction between times
                             Profit = cashOut - buyIn, 
                             profitPerHr = Profit/sesLength,
                             totalProfit = promoBonus + Profit,
                             totalProfitPerHr = totalProfit/sesLength, 
                             accuHour = cumsum(sesLength),
                             accuProfit = cumsum(Profit), 
                             accuProfitPerHr = accuProfit/accuHour,
                             accuTotalProfit = cumsum(totalProfit),
                             accuTotalProfitPerHr = accuTotalProfit/accuHour) 

options(tibble.width = Inf)  
#options(tibble.print_max = 15, tibble.print_min = 5) # if more than 15 rows, print 5 rows
Testimate


```

Tibble output options <https://r4ds.had.co.nz/tibbles.html> 10.3.1

<br>

#### A separate data set to be analyzed: Session with "The Course" mindset

```{r !DarkAge, Enlightend}
#Enlightened <- Testimate %>% filter(Date >= "2018-11-29") intuitive, but wrong, w.r.t cumulative values which are computed/had memory from overall dataset

EnlightenedEra <- GoogleSheet %>% mutate(Date = ymd(Date), #sesStart = ymd_hms(sesStart), sesEnd = ymd_hms(sesEnd),
                                  sesLength = round( as.numeric(sesEnd - sesStart), 2), #directly make substraction between times
                                  Profit = cashOut - buyIn, 
                                  profitPerHr = Profit/sesLength,
                                  totalProfit = promoBonus + Profit,
                                  totalProfitPerHr = totalProfit/sesLength) %>% 
                                  filter(Date >= "2018-11-29") %>% mutate(accuHour = cumsum(sesLength),
                                                                   accuProfit = cumsum(Profit), 
                                                                   accuProfitPerHr = accuProfit/accuHour,
                                                                   accuTotalProfit = cumsum(totalProfit),
                                                                   accuTotalProfitPerHr = accuTotalProfit/accuHour) 
options(tibble.width = Inf)  
#options(tibble.print_max = 15, tibble.print_min = 5) # if more than 15 rows, print 5 rows
EnlightenedEra
```



```{r Which day should I play? Total}
options(tibble.width = Inf)  

Testimate %>% 
  group_by(Day) %>%
  summarise(
    count = n(),
    sesLengthByDay = round( mean(sesLength),2),
    profitByDay = round(mean(Profit),2),
    profitPerHrByDay = round(mean(profitPerHr),2),
    totalProfitByDay = round(mean(totalProfit),2),
    totalProfitPerHrByDay = round(mean(totalProfitPerHr),2)
    ) %>% kable()

```

<br>


```{r Which day should I play? Enlightened Era}
options(tibble.width = Inf)  

EnlightenedEra %>% 
  group_by(Day) %>%
  summarise(
    count = n(),
    sesLengthByDay = round( mean(sesLength),2),
    profitByDay = round(mean(Profit),2),
    profitPerHrByDay = round(mean(profitPerHr),2),
    totalProfitByDay = round(mean(totalProfit),2),
    totalProfitPerHrByDay = round(mean(totalProfitPerHr),2)
    ) %>% kable()

```

<br>

### 2. Apply `htmlwidget` -> `highcharter`
<br>

#### Initially inspired by [Philipp Spachtholz](https://www.kaggle.com/philippsp/interactive-dashboards-in-r)

#### Package Author Joshua Kunst's RPub <https://rpubs.com/jbkunst/highcharter>

#### Additional `highcharter` learning material by [Danton Noriega](https://dantonnoriega.github.io/ultinomics.org/post/2017-04-05-highcharter-explainer.html) and [Nana Boateng](https://rstudio-pubs-static.s3.amazonaws.com/304105_70f2ad540827454e934117e3d90f6c1a.html)

<br>

#### A.1 Session Profit (Overall)

```{r}
#library(highcharter)

series = list(
  list(
    name = 'Total Profit for each session (promo bonus included), stratified by stake [yellow: 1/2, green: 1/3, lime: mix]',
    color = '#1E90FF', # <http://cloford.com/resources/colours/500col.htm>
    data = Testimate %>% select(totalProfit) %>% .[[1]]
  )
)

highchart() %>%
  hc_add_series_list(series) %>% 
  hc_xAxis(categories = Testimate %>% select(Day) %>% .[[1]], # or day
           plotBands = list(
             list(from = -0.5, to = 14.5, color = "#FFFACD"), # may be colored by day 
             list(from = 14.5, to = 15.5, color = "#BDFCC9"),
             list(from = 15.5, to = 16.5, color = "#FFFACD"),
             list(from = 16.5, to = 17.5, color = "#CAFF70"),
             list(from = 17.5, to = 18.5, color = "#CAFF70"),
             list(from = 18.5, to = 19.5, color = "#FFFACD")
             )) %>%
  hc_yAxis(plotLines = list(
             list(value = 0, width = 3, color = 'black')
           ))
    
```

<br>

#### A.2 Session Profit (Enlightened Era)

```{r}
series = list(
  list(
    name = 'Total Profit for each session in Enlightened Era (promo bonus included), stratified by stake [yellow: 1/2, green: 1/3, lime: mix]',
    color = '#1E90FF', # <http://cloford.com/resources/colours/500col.htm>
    data = EnlightenedEra %>% select(totalProfit) %>% .[[1]]
  )
)

highchart() %>%
  hc_add_series_list(series) %>% 
  hc_xAxis(categories = EnlightenedEra %>% select(Day) %>% .[[1]], # or day
           plotBands = list(
             list(from = -0.5, to = 0.5, color = "#FFFACD"), 
             list(from = 0.5, to = 1.5, color = "#BDFCC9"),
             list(from = 1.5, to = 2.5, color = "#FFFACD"),
             list(from = 2.5, to = 3.5, color = "#CAFF70"),
             list(from = 3.5, to = 4.5, color = "#CAFF70"),
             list(from = 4.5, to = 5.5, color = "#FFFACD")
             )) %>%
  hc_yAxis(plotLines = list(
             list(value = 0, width = 3, color = 'black')
           ))
    
```


<br>

#### B.1 Cumulative Profit (Overall)

```{r}
series = list(
  list(
    name = 'Cumulative Profit',
    color = '#EEAD0E', 
    data = Testimate %>% select(accuProfit) %>% .[[1]]
  ),
  list(
    name = 'Cumulative Total Profit (promo bonus included)',
    color = '#FF7D40', 
    data = Testimate %>% select(accuTotalProfit) %>% .[[1]]
  )
)

highchart() %>%
  hc_add_series_list(series) %>% hc_xAxis(categories = Testimate %>% select(Day) %>% .[[1]],
                                          plotBands = list(
                                            list(from = -0.5, to = 14.5, color = "#FFFACD"),
                                            list(from = 14.5, to = 15.5, color = "#BDFCC9"),
                                            list(from = 15.5, to = 16.5, color = "#FFFACD"),
                                            list(from = 16.5, to = 17.5, color = "#CAFF70"),
                                            list(from = 17.5, to = 18.5, color = "#CAFF70"),
                                            list(from = 18.5, to = 19.5, color = "#FFFACD")
                                            ))
```

<br>

#### B.2 Cumulative Profit (Enlightened)

```{r}
series = list(
  list(
    name = 'Cumulative Profit in Enlightened Era',
    color = '#EEAD0E', 
    data = EnlightenedEra %>% select(accuProfit) %>% .[[1]]
  ),
  list(
    name = 'Cumulative Total Profit in Enlightened Era (promo bonus included)',
    color = '#FF7D40', 
    data = EnlightenedEra %>% select(accuTotalProfit) %>% .[[1]]
  )
)

highchart() %>%
  hc_add_series_list(series) %>% hc_xAxis(categories = EnlightenedEra %>% select(Day) %>% .[[1]],
                                          plotBands = list(
                                            list(from = -0.5, to = 0.5, color = "#FFFACD"),  
                                            list(from = 0.5, to = 1.5, color = "#BDFCC9"),
                                            list(from = 1.5, to = 2.5, color = "#FFFACD"),
                                            list(from = 2.5, to = 3.5, color = "#CAFF70"),
                                            list(from = 3.5, to = 4.5, color = "#CAFF70"),
                                            list(from = 4.5, to = 5.5, color = "#FFFACD")
                                            ))
```

<br>

#### C.1 Cumulative Profit per hour Rate (Overall)

```{r}
series = list(
  list(
    name = 'Cumulative Profit Per Hour',
    color = '#EEAD0E',
    data = Testimate %>% select(accuProfitPerHr) %>% .[[1]] %>% round(2) 
  ),
  list(
    name = 'Cumulative Total Profit Per Hour (promo bonus included)',
    color = '#FF7D40',
    data = Testimate %>% select(accuTotalProfitPerHr) %>% .[[1]] %>% round(2)
  )
)

highchart() %>%
  hc_add_series_list(series) %>% hc_xAxis(categories = Testimate %>% select(Day) %>% .[[1]],
                                          plotBands = list(
                                            list(from = -0.5, to = 14.5, color = "#FFFACD"),
                                            list(from = 14.5, to = 15.5, color = "#BDFCC9"),
                                            list(from = 15.5, to = 16.5, color = "#FFFACD"),
                                            list(from = 16.5, to = 17.5, color = "#CAFF70"),
                                            list(from = 17.5, to = 18.5, color = "#CAFF70"),
                                            list(from = 18.5, to = 19.5, color = "#FFFACD")
                                            ))
```

<br>

#### C.2 Cumulative Profit per hour rate (Enlightened)

```{r}
series = list(
  list(
    name = 'Cumulative Profit Per Hour in Enlightened Era',
    color = '#EEAD0E',
    data = EnlightenedEra %>% select(accuProfitPerHr) %>% .[[1]] %>% round(2) 
  ),
  list(
    name = 'Cumulative Total Profit Per Hour in Enlightened Era (promo bonus included)',
    color = '#FF7D40',
    data = EnlightenedEra %>% select(accuTotalProfitPerHr) %>% .[[1]] %>% round(2)
  )
)

highchart() %>%
  hc_add_series_list(series) %>% hc_xAxis(categories = EnlightenedEra %>% select(Day) %>% .[[1]],
                                          plotBands = list(
                                            list(from = -0.5, to = 0.5, color = "#FFFACD"),  
                                            list(from = 0.5, to = 1.5, color = "#BDFCC9"),
                                            list(from = 1.5, to = 2.5, color = "#FFFACD"),
                                            list(from = 2.5, to = 3.5, color = "#CAFF70"),
                                            list(from = 3.5, to = 4.5, color = "#CAFF70"),
                                            list(from = 4.5, to = 5.5, color = "#FFFACD")
                                            ))
```

`highcharter` seems to be outdated on CRAN. Directly install from github via

```
library(devtools)
install_github("jbkunst/highcharter")
```

